PyPy: raising the level for Dynamic Language implementations

### 2007-05-27 talk/dyla2007/dyla.tex
slight rewrite of the first paragraph of the abstract. adding a parenthetical comment about GCs.

We argue in this paper that one should not write interpreters manually but
rather use meta-programming techniques and raise the overall level at which
dynamic languages are implemented. We believe this to be ultimately a better
investment of efforts than the development of more advanced general-purpose OO
VMs.

@@

For these reasons writing a virtual machine in C is problematic because it
forces the language implementer to deal with many low-level details. Limitations
of the C implementation lead to alternative implementations which draw
work-power from the reference implementation. An alternative to writing
implementations in C is to build them on top of one of the newer object oriented
virtual machines (``OO VM'') such as the JVM or the CLR. This is often wanted by
the community anyway, since it leads to better re-usability of libraries of
these platforms. However, if a C implementation existed before the
implementation of such a VM is started, this enters in conflict with the goal of
having to maintain essentially a single, simple enough implementation for a
given programming language: as the language becomes popular, there will be a
demand for having it run on various platforms -- high-level VMs as well as
C-level environments.

>>>>

We argue in this paper that one should not write interpreters for dynamic
languages manually but rather use meta-programming techniques and raise the
overall level at which they are are implemented. We believe this to be
ultimately a better investment of efforts than the development of more advanced
general-purpose object oriented VMs.

@@

For these reasons writing a virtual machine in C is problematic because it
forces the language implementer to deal with many low-level details (like
garbage collection and threading-issues). Limitations
of the C implementation lead to alternative implementations which draw
work-power from the reference implementation. An alternative to writing
implementations in C is to build them on top of one of the newer object oriented
virtual machines (``OO VM'') such as the JVM or the CLR. This is often wanted by
the community anyway, since it leads to better re-usability of libraries of
these platforms. However, if a C implementation existed before the
implementation of such a VM is started, this enters in conflict with the goal of
having to maintain essentially a single, simple enough implementation for a
given programming language: as the language becomes popular, there will be a
demand for having it run on various platforms -- high-level VMs as well as
C-level environments.
